Brief Announcement: An Improved Lower Bound for Dynamic Graph Partitioning

### 2020-01-29 paper/paper.tex
introduction

Main technical contribution of this paper is $\Omega(k\ell)$ lower bound for the competitive ratio of any deterministic algorithm for Online Balanced Partition problem.
The best known lower bound so far was $\Omega(k)$ \cite{repartition-disc}.

Additionally, we contribute to search for the optimal algorithm by presenting $O(k\ell)$-competitive algorithm for the special case, where the perfect partition of the input graph is assumed, and every algorithm must colocate every communicating pair.
Note that our $\Omega(k\ell)$ lower bound uses a perfect partition input graph and colocates communicating pairs, and hence for this scenario, our results are tight.
\maciek{Also, it is easy to construct the adversary that forces collocation of requested nodes}

>>>>

Main technical contribution of this paper is the lower bound $\Omega(k\ell)$ for the competitive ratio of any deterministic algorithm for Online Balanced Partition problem.
The best known lower bound so far was $\Omega(k)$ \cite{repartition-disc}
which involves only two cluster.

Additionally, we contribute to the research on the optimal online algorithm by presenting a $O(k\ell)$-competitive algorithm for the special case
where the communication graph (i.e., request sequence) admits a \emph{perfect partition},
i.e., a (multi-way) cut of cost zero that is also an optimal partition for the offline problem.
%and every algorithm must colocate every communicating pair.
Note that our $\Omega(k\ell)$ lower bound generates the input sequence
so that the optimal offline choice is a perfect partition.
\maciek{Also, it is easy to construct the adversary that forces collocation of requested nodes
\mahmoud{this is already the case in the lower bound proof. Do we still need the last sentence here?}
}
